The problem and promise of scale in multilayer networks

### 2019-09-20 paper/unstructured.Rmd
add table 1 draft

### Introduction?
We determined three types of multilayer networks most relevant to spatial variables
Multilayer networks with layers defined by spatially explicit locations, interspecific interactions, and community or subpopulation structure. 
Other types of networks, such as intercontexual networks or temporal networks, are likely only to incorporate spatial variables in a hybrid multilayer network and considerations for including those variables will be explored here

>>>>

### Introduction?
We determined three types of multilayer networks most relevant to spatial variables. Multilayer networks with layers defined by spatially explicit locations, interspecific interactions, and community or subpopulation structure. 
Other types of networks, such as intercontexual networks or temporal networks, are likely only to incorporate spatial variables in a hybrid multilayer network and considerations for including those variables will be explored here

### Table 1

|               | Spatial                                                           | Net of nets                                      | Interspecific                                              |
|---------------|-------------------------------------------------------------------|--------------------------------------------------|------------------------------------------------------------|
| layer         | spatially explicit                                                | subpops, fuzzy patches                           | dif species                                                |
| node          | individuals                                                       | ind + nets                                       | ind + species nets                                         |
| inter edges   | to self                                                           | to nets                                          | to species                                                 |
| intra edges   | association to other                                              | association                                      | association                                                |
| social grain  | type of interaction, chain rule, spatsoc threshold, hyena session | for intra, see left. for inter: define community |  for intra, see left. for inter: similarity, vulnerability |
| spatial grain | resolution                                                        | patches, k=                                      | connectivity, clusters                                     |
